---
title: "Blueprint for halving obesity in the UK"
Author: Anish Chacko
Organisation: Nesta
output: html_notebook
---

### Policy Tranche 1

List of policies included:

| Policy ID | Policy Title                                                                                                                                                                  |
|------------------|------------------------------------------------------|
| 1         | Restrict screen (TV and online) advertising for HFSS products through introduction of a 2100-0530 watershed and restrictions on online paid advertising                       |
| 2         | Restrict all outdoor advertising on public transport (i.e. all bus stops, train stations and tube stations, implemented via national regulation)                              |
| 6         | Everyone with a BMI of 30 or above is offered a free referral to a behavioural weight loss programme (either 12-month TDR or 12-week education) via a primary care clinician. |
| 7         | Enforce provision of nutri-score front-of-pack labelling on retail packaging                                                                                                  |
| 9         | Mandate maximum calorie per single serve portion guidelines for the OOH sector                                                                                                |
| 8a        | Fund and roll out a mass media campaign aiming to promote healthy eating                                                                                                      |
| 23        | Restricting Checkout, End-of-Aisle, and Store Entrance Sales of Food and Drinks High in Fat, Salt, and Sugar (HFSS)                                                           |

Calling libraries, functions and dataframes to be used later in the code:

```{r}
library(here)

source(file = "C:/git/ahl_obesity_blueprint/requirements.R")

getwd()


source(file = "models/adult_model_calorie.R")
source(file = "pre_processing/pre_processing_adult.R")

```

Policy 9: Mandate maximum calorie per single serve portion guidelines for the out of home sector

The policy mandates all out of home businesses to reduce the calorie content of their products to meet the maximum calorie guidelines. A similar policy, on a voluntary basis, was proposed by Public Health England (PHE) under their [Calorie reduction programme](https://www.gov.uk/government/publications/calorie-reduction-guidelines-for-the-food-industry). The PHE guidelines indicate that for out of home businesses the target was to reduce the calorie content by 20% of the average calorie content of single serve portions.

The evidence from the [rapid review](https://docs.google.com/document/d/1Mc9UahGny4g-gO_8mIzEHmMSgTQhhzZuDQ1Y-CQfYeg/edit?usp=sharing) (quality assured by the EAG) that identified a meta-analysis showed that a 40% reduction in portion sizes of products led to a reduction of 247 kcals in daily energy intake. In case of this policy, for a 20% reduction, we assume that the reduction in daily energy intake is approximately half of that reported by the review, that is 123.5 kcals `(intake_change)`.

Estimating the prevalence of obesity

```{r}

process_clean_save(file_path = here("inputs/raw/hse_2019_eul_20211006.tab"),
                   nation = "England")


input_df = read_csv(here("inputs/processed/hse_2019.csv"))
intake_change = -123.5
implmnt_duration = 365*5


adult_model_op = calculate_bmi_from_eichange(df = input_df,

intake_change = intake_change, implmentation_duration = implmnt_duration)

```

```{r}



adult_model_op$bmi_category_plot

adult_model_op$bmi_percent_prevalence

adult_model_op$category_plot






```

```{r}

adult_model_op$bmi_percent_prevalence  
```

```{r}

adult_model_op$category_plot
```
